Enhancing \Hinf{} Norm Estimation using Local LPM/LRM Modeling: Applied to an AVIS\thanksref{thx}

### 2016-05-09 ch01-intro/introduction.tex
Some improvements in figures, consistency

\chapter{Introduction}
\def\thisDir{ch01-intro}
\tikzsetfigurename{ch01fig}
\glsresetall
\myEpigraph{It's a dangerous business, Frodo, going out your door. You step onto the road, and if you don't keep your feet, there's no knowing where you might be swept off to.}{John Ronald Reuel Tolkien}{The Fellowship of the Ring}

@@

\paragraph{White box}
On the one hand, there is so-called \term{`white box'} modeling, or first-principles modeling.
The model is constructed by writing down the equations that govern the system, e.g. Newton's laws of motion for mechanical systems, Kirchoff's laws for electrical circuits, \latin{etc.}
This is the kind of modeling that is practiced in school, which explains why it is also popular in industry.
Unfortunately, white box modeling quickly becomes unwieldy once more complicated systems are to be studied or many parts of the system are uncertain.
In general, lot of man-hours are required to build a white box model, such that this is often prohibitively expensive for engineering applications.

>>>>

\chapter{Introduction}
\def\thisDir{ch01-intro}
\tikzsetfigurename{ch01fig}
\glsresetall{}
\myEpigraph{It's a dangerous business, Frodo, going out your door. You step onto the road, and if you don't keep your feet, there's no knowing where you might be swept off to.}{John Ronald Reuel Tolkien}{The Fellowship of the Ring}

@@

\paragraph{White box}
On the one hand, there is so-called \term{`white box'} modeling, or first-principles modeling.
The model is constructed by writing down the equations that govern the system, e.g. Newton's laws of motion for mechanical systems, Kirchhoff's laws for electrical circuits, \latin{etc.}
This is the kind of modeling that is practiced in school, which explains why it is also popular in industry.
Unfortunately, white box modeling quickly becomes unwieldy once more complicated systems are to be studied or many parts of the system are uncertain.
In general, lot of man-hours are required to build a white box model, such that this is often prohibitively expensive for engineering applications.

### 2016-05-09 ch03-lrm/nonparametric.tex
Some improvements in figures, consistency

\chapter{Non-parametric Modeling}
\def\thisDir{ch03-lrm}
\tikzsetfigurename{ch03fig}
\label{sec:nonparametric}
\myEpigraph{I love deadlines. I like the whooshing sound they make as they fly by.}{Douglas Adams}{}
\glsresetall

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{1.24\figurewidth}
  \input{ch03-lrm/figs/tune-NBW3-pressAndNoise.tikz}
  \caption[Output spectrum for local modeling, together the PRESS statistic]{It is convenient to compare the \glsentryshort{PRESS} (left plots) and the noise variance (right plots). The theoretical noise level is shaded and the transfer function is shown in bold.}
  \label{fig:nparam:PRESS}
\end{figure}

For the high \gls{SNR} case, it can be seen in \figref{fig:nparam:PRESS} that the \gls{LPM} is heavily biased and hence results in a large overestimate of the noise variance near the resonance peak.
As a result, the \gls{PRESS} in the same region is also elevated for the \gls{LPM}.
Outside the resonance peak, the \gls{LPM} and \gls{LRM} estimate very similar noise variances.
The \gls{PRESS} the different methods are in agreement with the observations regarding the \gls{RMS} error from the Monte Carlo simulations in \figref{fig:nparam:comparison:midSNR}: all tested \gls{LRM} perform similarly (with a slight advantage for the first-order method), the \gls{LPM} produces much larger errors near the resonance.
Nevertheless, this figure illustrates that for the \gls{LRM}, the error is quite flat over the frequency.
Note also that the \gls{PRESS} suffers from a quite high variance over the frequency, which is a well-known drawback~\citep{Seber2003,Arlot2010}.

For the low \gls{SNR} case (top plots in  \figref{fig:nparam:PRESS} ), it can be seen that both \gls{LPM} and \gls{LRM} result in a very similar estimate of the noise level.
The values of the \gls{PRESS} are again quite noisy.
\TODO{PRESS is eigenlijk niet bruikbaar bij lage SNR}

@@

\section{Conclusions}
\label{sec:conclusion}
In this chapter, the performance of non-parametric \gls{LPM} and \gls{LRM} estimators were compared to observe the \gls{FRF} of resonant systems.
Since the \gls{LRM} is a biased estimator while the \gls{LPM} is asymptotically unbiased, it is important to compare their behavior.
Hence, expressions for the bias of the \gls{LRM} were derived.
%TODO: tom: "inherently biased": verregaande uitspraak in relatie met Levy: is normaal ook biased, maar voor ARX niet. Hoe zit dat hier?
For good \glspl{SNR} in resonant systems, it was seen that the \gls{LRM} is always superior to the \gls{LPM}.
For extremely poor \gls{SNR}, i.e. $\SNR \approx 10\unit{dB}$, the \gls{LPM} may perform slightly better than the \gls{LRM} when short measurement records are available.
In this chapter, the \gls{LRIC} was introduced.
This is an extension of the \gls{LRM} which solves the non-linear optimization problem and should thus be able to avoid a bias altogether.
However, it is seen that this estimator is extremely noisy but seems to provide a smaller bias than the \gls{LRM}.
Since the overall \gls{RMS} error for the \gls{LRIC} is much larger than most other methods, the \gls{LRIC} cannot be used in its current form.

>>>>

\chapter{Non-parametric Modeling}
\def\thisDir{ch03-lrm}
\tikzsetfigurename{ch03fig}
\label{sec:nonparametric}
\myEpigraph{I love deadlines. I like the whooshing sound they make as they fly by.}{Douglas Adams}{}
\glsresetall{}

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{1.24\figurewidth}
  \input{ch03-lrm/figs/tune-NBW3-pressAndNoise.tikz}
  \caption[Example: \glsentryshort{PRESS} and noise spectrum]{It is convenient to compare the \glsentryshort{PRESS} (left plots) and the noise variance (right plots) when good \gls{SNR} is available. The theoretical noise level is shaded and the transfer function is shown in bold.}
  \label{fig:nparam:PRESS}
\end{figure}

For the high \gls{SNR} case, it can be seen in \figref{fig:nparam:PRESS} that the \gls{LPM} is heavily biased and hence results in a large overestimate of the noise variance near the resonance peak.
As a result, the \gls{PRESS} in the same region is also elevated for the \gls{LPM}.
Outside the resonance peak, the \gls{LPM} and \gls{LRM} estimate very similar noise variances.
The \gls{PRESS} the different methods are in agreement with the observations regarding the \gls{RMS} error from the Monte Carlo simulations in \figref{fig:nparam:comparison:midSNR}: all tested \gls{LRM} perform similarly (with a slight advantage for the first-order method), the \gls{LPM} produces much larger errors near the resonance.
Nevertheless, this figure illustrates that for the \gls{LRM}, the error is quite flat over the frequency.
Note also that the \gls{PRESS} suffers from a quite high variance over the frequency, which is a well-known drawback~\citep{Arlot2010}.

For the low \gls{SNR} case (top plots in  \figref{fig:nparam:PRESS} ), it can be seen that both \gls{LPM} and \gls{LRM} result in a very similar estimate of the noise level.
The values of the \gls{PRESS} are again very noisy.
\TODO{PRESS is eigenlijk niet bruikbaar bij lage SNR}

@@

\section{Conclusions}
\label{sec:conclusion}
In this chapter, the performance of non-parametric \gls{LPM} and \gls{LRM} estimators were compared to observe the \gls{FRF} of resonant systems.
Since the \gls{LRM} is a biased estimator while the \gls{LPM} is asymptotically unbiased, it is important to compare their behavior.
Hence, expressions for the bias of the \gls{LRM} were derived.
For good \glspl{SNR} in resonant systems, it was seen that the \gls{LRM} is always superior to the \gls{LPM}.
For extremely poor \gls{SNR}, i.e. $\SNR \approx 10\unit{dB}$, the \gls{LPM} may perform slightly better than the \gls{LRM} when short measurement records are available.
In this chapter, the \gls{LRIC} was introduced.
This is an extension of the \gls{LRM} which solves the non-linear optimization problem and should thus be able to avoid a bias altogether.
However, it is seen that this estimator is extremely noisy but seems to provide a smaller bias than the \gls{LRM}.
Since the overall \gls{RMS} error for the \gls{LRIC} is much larger than most other methods, the \gls{LRIC} cannot be used in its current form.

### 2016-05-09 ch04-lrmhinf/lrmhinf.tex
Clean up math + SNR in FD in ch04
Some improvements in figures, consistency

\chapter{Non-parametric Peak Modeling}
\label{sec:hinf}
\def\thisDir{ch04-lrmhinf}
\tikzsetfigurename{ch04fig}
\myEpigraph{Design is not just what it looks like and feels like. Design is how it works.}{Steve Jobs}{}
\researchBasedOn{Geerardyn2014IFAC,Geerardyn2014ISMA}
\glsresetall

@@

% \section{Introduction}
% \label{sec:lrmhinf:Intro}

@@

Although important steps have been made in model-error-modeling, existing methods involve a trade-off between accuracy, measurement time, and user intervention.
The aim of this chapter is to develop a golden mean between traditional non-parametric techniques (third approach) and a full parametric model (second approach).
The proposed $\Hinf{}$ norm estimation procedure exploits recent developments in frequency domain estimation using the \gls{LPM} \citep{Schoukens2009LPM} and the \gls{LRM} \citep{McKelvey2012LRM} as introduced in \citet{Geerardyn2014IFAC,Geerardyn2014ISMA}.
Before, these \gls{LPM} and \gls{LRM} techniques have been used to enhance at-grid frequency response estimates.
Here, these methods are extended to provide both an at-grid and inter-grid evaluation of the maximum singular value near resonances, as is required for the $\Hinf{}$ norm and consequently the design of robust controllers.
The performance of these local parametric models in the context of robust control design is investigated, and bounds on the required measurement time to obtain a reliable estimate of the \Hinf{} norm are obtained.
% Preliminary results appear in~\citep{Geerardyn2014IFAC,Geerardyn2014ISMA}.
% This paper presents the full procedure, including more theoretical treatment of the $\Hinf{}$ norm estimation procedure, and a description of the required measurement time.

@@

%\glsresetall

@@

We denote $\lrm{N_W,N_B,N_A,N_T}$ to be the \gls{LRM} with the orders $N_B$, $N_A$, $N_T$ and bandwidth $N_W$ defined above.
For $N_A=0$ the \gls{LRM} simplifies to the \gls{LPM} which we shall denote as $\lpm{N_W,N_B,N_T}$.

@@

\subsection{A Concrete Simulation}
Consider a discrete time system $\Delta$ (see \figref{fig:lrmhinf:exampleIntergrid}) as unmodeled dynamics in an output-error setting:
\begin{equation}
  \Delta(z) 
    =  \frac{0.45373 z + 0.44752}
            {z^2 - 1.0595 z + 0.96079}
  \label{eq:lrmhinf:O2sysDT}
  \text{,}
\end{equation}
which has $\timeconst = 50 \unit{samples}$ (i.e. $\damping=0.02$ and $\wn = 1 \unit{rad/s}$).
The input signal $u_{\Delta}$ is white Gaussian noise with unit variance and the disturbing noise variance $\sigma_v^2$ is chosen such that a \gls{SNR} 
\begin{equation}
  \SNR = \frac{\sqrt{\inv{N}\sum_n y_{\Delta0}^2(n) }}%
              {\sqrt{\inv{N}\sum_n v^2(n) }}
       = \frac{\sigma_{y_{\Delta0}}}{\sigma_v}
       \approx \frac{\norm[2]{\Delta} \sigma_{u_{\Delta}}}{\sigma_v}
  \label{eq:lrmhinf:SNR}
\end{equation}
of $10$ is obtained.
%TODO: give the SNR also in frequency domain

Classical \gls{SA} techniques~\citep{Bendat1993} can estimate the \gls{FRF} of $\Delta$.
This is done by first splitting the input and output signals ($u(n)$ and $y(n)$)  into $\nSegments$ segments of $N/\nSegments$ samples that we will denote as
\begin{equation}
  x^{[i]}(n) = x\left( (i-1) \nSegments + n \right) 
  \text{ with }
  n \in \set{0, \ldots N/\nSegments - 1}
  \text{ and }
  i \in \set{1, \ldots, \nSegments}
  \text{.}
  \label{eq:lrmhinf:SA:segmentation}
\end{equation}
Each of these segments is windowed using a function $w_{N/\nSegments}(n)$ to reduce leakage such that 
\begin{equation}
x^{[i]}_{w}(n) = x^{[i]}(n) \cdot w_{N/\nSegments}(n)
\text{.}
\end{equation}
The frequency domain counterparts are obtained by means of the \gls{DFT}, and are denoted 
\begin{equation}
X^{[i]}_W(k) = \DFT(x^{[i]}_w(n))
\text{,}
\end{equation}
where it should be noted that $k \in \set{0,N/\nSegments}$ such that the frequency resolution is $\frac{2\pi \nSegments}{N}$.
By dividing the resulting auto- and cross-spectra, the \gls{FRF} of $\Delta$ can be estimated
\begin{equation}
  \hat{\Delta}_{\mathrm{SA}}(k) \isdef 
  \frac{\frac{1}{\nSegments} \Sum_{i=1}^{\nSegments} Y_W^{[i]}(k) \conj{U_{W}^{[i]}(k)} }
           {\frac{1}{\nSegments} \Sum_{i=1}^{\nSegments} U_W^{[i]}(k) \conj{U_{W}^{[i]}(k)} }
  \
\end{equation}
In this chapter a Hann window ($w_{N/\nSegments}(n) = \sin^2 (\frac{\pi n}{N/\nSegments -1})$) and $\nSegments=1$ are used.
Note that $\nSegments>1$  increases the measurement time by a factor $\nSegments$ to attain the same frequency resolution (but would improve transient and noise rejection).

\figref{fig:lrmhinf:exampleIntergrid} illustrates for $N=97$ that $\gamma_{\mathrm{FRF}}$ for the \gls{SA}, $\lpm{5,4,4}$ and $\lrm{5,2,2,2}$ approaches yield unreliable estimates of $\infnorm{\Delta}$, since the frequency resolution is too coarse.
The specific orders of  \gls{LRM}/\gls{LPM} have been chosen to  keep $N_W$ small while not restricting ourselves to local linear models ($N_B=1$). 
Slightly different orders (e.g. $\lrm{4,1,1,1}$) yield comparable results.

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.75\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/figs/example-both.tikz}
  %\input{\thisDir/figs/example-LRM-SNR1.tikz}
  \caption[Example: FRF underestimates $\E{\gamma}$]{Simulation example revealing that $\gamma_{\mathrm{FRF}}$ (left) for both the \glsfirst{SA}~\legref{leg:example-SA} and \gls{LRM}~\legref{leg:example-LRM} underestimate the true $\gamma = \infnorm{\Delta} = 24$~\legref{leg:example-true-Hinf} due to limited frequency resolution.
  Using the proposed \gls{LRM}-based approach, both the at-grid~($\gamma_{\mathrm{FRF}}$) and intergrid~($\gammaIntergrid$) estimate are improved.
  The interpolated \gls{LRM}~\legref{leg:example-LRM-interpol} and true $\Delta$~\legref{leg:example-true} almost coincide.
  Hence, $\widehat{\infnorm{\Delta_{\mathrm{LRM}}}}_{\infty}$~\legref{leg:example-LRM-interpol-Hinf} approaches the theoretical $\gamma=24$.}
  \label{fig:lrmhinf:exampleIntergrid}
\end{figure}

It can be observed for $\gammaIntergrid$ in \figref{fig:lrmhinf:exampleIntergrid} that the \gls{LRM} is able to model the resonance well and yields a useful estimate $\infnorm{\Delta_{\mathrm{LRM}}} = 24$ in the simulation.
Intuitively, the \gls{LRM} locally approximates the resonant pole which allows for a reliable inter-grid estimate.
The \gls{LPM}, on the other hand, does not provide a reliable estimate.

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.75\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/figs/MC-runlength.tikz}
  %\input{figures/runLength.tikz}
  \caption[Estimated $\gamma$ versus measurement time.]{This Monte Carlo simulation shows that the $\Hinf{}$ norm~\legref{leg:runlength-true} is underestimated significantly for short experiments ($N<20\timeconst$) by $\expectedValue{\gammaAtGrid}$~\legref{leg:runlength-frf} and the \gls{LPM}~\legref{leg:runlength-LPM}.
  However, the proposed $\widehat{\infnorm{\Delta_{\mathrm{LRM}}}}$~\legref{leg:runlength-LRM} is already reliable from much shorter experiments ($N \geq 4 \timeconst$). A single observation for $N=97$~\legref{leg:runlength-special-case} is shown in \figref{fig:lrmhinf:exampleIntergrid}. The shaded areas show the $\pm \sigma$ intervals which are due to the noise.
  }
\label{fig:lrmhinf:MC-run-length}
\end{figure}

>>>>

\chapter{Non-parametric Peak Modeling}
\label{sec:hinf}
\def\thisDir{ch04-lrmhinf}
\tikzsetfigurename{ch04fig}
\myEpigraph{Design is not just what it looks like and feels like. Design is how it works.}{Steve Jobs}{}
\researchBasedOn{Geerardyn2014IFAC,Geerardyn2014ISMA}
\glsresetall{}

@@

@@

Although important steps have been made in model-error-modeling, existing methods involve a trade-off between accuracy, measurement time, and user intervention.
The aim of this chapter is to develop a golden mean between traditional non-parametric techniques (third approach) and a full parametric model (second approach).
The proposed $\Hinf{}$ norm estimation procedure exploits recent developments in frequency domain estimation using the \gls{LPM} \citep{Schoukens2009LPM} and the \gls{LRM} \citep{McKelvey2012LRM} as introduced in \citet{Geerardyn2014IFAC,Geerardyn2014ISMA}.
Before, these \gls{LPM} and \gls{LRM} techniques have been used to enhance at-grid frequency response estimates.
Here, these methods are extended to provide both an at-grid and inter-grid evaluation of the maximum singular value near resonances, as is required for the $\Hinf{}$ norm and consequently the design of robust controllers.
The performance of these local parametric models in the context of robust control design is investigated, and bounds on the required measurement time to obtain a reliable estimate of the \Hinf{} norm are obtained.

@@

@@

We denote $\lrm{N_W,\order{B},\order{A},\order{T}}$ to be the \gls{LRM} with the orders $\order{B}$, $\order{A}$, $\order{T}$ and bandwidth $N_W$ defined above.
For $\order{A}=0$ the \gls{LRM} simplifies to the \gls{LPM} which we shall denote as $\lpm{N_W,\order{B},\order{T}}$.

@@

\subsection{A Concrete Simulation}
Consider a discrete time system $\Delta$ (see \figref{fig:lrmhinf:exampleIntergrid}) as unmodeled dynamics in an output-error setting:
\begin{equation}
  \Delta(z) 
    =  \frac{0.45373 z + 0.44752}
            {z^2 - 1.0595 z + 0.96079}
  \label{eq:lrmhinf:O2sysDT}
  \text{,}
\end{equation}
which has $\timeconst = 50 \unit{samples}$ (i.e. $\damping=0.02$ and $\wn = 1 \unit{rad/s}$).
The input signal $u_{\Delta}$ is white Gaussian noise with unit variance and the disturbing noise variance $\sigma_v^2$ is chosen such that a \gls{SNR} 
\begin{equation}
  \SNR = \frac{\sqrt{\inv{N}\sum_n y_{\Delta0}^2(n) }}%
              {\sqrt{\inv{N}\sum_n v^2(n) }}
       = \frac{\sigma_{y_{\Delta0}}}{\sigma_v}
       \approx \frac{\norm[2]{\Delta} \sigma_{u_{\Delta}}}{\sigma_v}
  \label{eq:lrmhinf:SNR}
\end{equation}
of $10$ is obtained.
In the frequency domain, this corresponds to $\SNR_{\BW} \approx 26 \unit{dB}$ in the $3\unit{dB}$ bandwidth of this resonance peak.

Classical \gls{SA} techniques~\citep{Bendat1993} can estimate the \gls{FRF} of $\Delta$.
This is done by first splitting the input and output signals ($u(n)$ and $y(n)$)  into $\nSegments$ segments of $N/\nSegments$ samples that we will denote as
\begin{equation}
  x^{[i]}(n) = x\left( (i-1) \nSegments + n \right) 
  \text{ with }
  n \in \set{0, \ldots N/\nSegments - 1}
  \text{ and }
  i \in \set{1, \ldots, \nSegments}
  \text{.}
  \label{eq:lrmhinf:SA:segmentation}
\end{equation}
Each of these segments is windowed using a function $w_{N/\nSegments}(n)$ to reduce leakage such that 
\begin{equation}
x^{[i]}_{w}(n) = x^{[i]}(n) \cdot w_{N/\nSegments}(n)
\text{.}
\end{equation}
The frequency domain counterparts are obtained by means of the \gls{DFT}, and are denoted 
\begin{equation}
X^{[i]}_W(k) = \DFT(x^{[i]}_w(n))
\text{,}
\end{equation}
where it should be noted that $k \in \set{0,N/\nSegments}$ such that the frequency resolution is $\frac{2\pi \nSegments}{N}$.
By dividing the resulting auto- and cross-spectra, the \gls{FRF} of $\Delta$ can be estimated
\begin{equation}
  \hat{\Delta}_{\mathrm{SA}}(k) \isdef 
  \frac{\frac{1}{\nSegments} \Sum_{i=1}^{\nSegments} Y_W^{[i]}(k) \conj{U_{W}^{[i]}(k)} }
           {\frac{1}{\nSegments} \Sum_{i=1}^{\nSegments} U_W^{[i]}(k) \conj{U_{W}^{[i]}(k)} }
\end{equation}
In this chapter a Hann window ($w_{N/\nSegments}(n) = \sin^2 (\frac{\pi n}{N/\nSegments -1})$) and $\nSegments=1$ are used.
Note that $\nSegments>1$  increases the measurement time by a factor $\nSegments$ to attain the same frequency resolution (but would improve transient and noise rejection).

\figref{fig:lrmhinf:exampleIntergrid} illustrates for $N=97$ that $\gamma_{\mathrm{FRF}}$ for the \gls{SA}, $\lpm{5,4,4}$ and $\lrm{5,2,2,2}$ approaches yield unreliable estimates of $\infnorm{\Delta}$, since the frequency resolution is too coarse.
The specific orders of  \gls{LRM}/\gls{LPM} have been chosen to  keep $N_W$ small while not restricting ourselves to local linear models ($\order{B}=1$). 
Slightly different orders (e.g. $\lrm{4,1,1,1}$) yield comparable results.

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.75\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/figs/example-both.tikz}
  \caption[Example: \glsentryshort{FRF} underestimates $\E{\gamma}$]{Simulation example revealing that $\gamma_{\mathrm{FRF}}$ (left) for both the \glsfirst{SA}~\legref{leg:example-SA} and \gls{LRM}~\legref{leg:example-LRM} underestimate the true $\gamma = \infnorm{\Delta} = 24$~\legref{leg:example-true-Hinf} due to limited frequency resolution.
  Using the proposed \gls{LRM}-based approach, both the at-grid~($\gamma_{\mathrm{FRF}}$) and intergrid~($\gammaIntergrid$) estimate are improved.
  The interpolated \gls{LRM}~\legref{leg:example-LRM-interpol} and true $\Delta$~\legref{leg:example-true} almost coincide.
  Hence, $\widehat{\infnorm{\Delta_{\LRM}}}_{\infty}$~\legref{leg:example-LRM-interpol-Hinf} approaches the theoretical $\gamma=24$.}
  \label{fig:lrmhinf:exampleIntergrid}
\end{figure}

It can be observed for $\gammaIntergrid$ in \figref{fig:lrmhinf:exampleIntergrid} that the \gls{LRM} is able to model the resonance well and yields a useful estimate $\infnorm{\Delta_{\LRM}} = 24$ in the simulation.
Intuitively, the \gls{LRM} locally approximates the resonant pole which allows for a reliable inter-grid estimate.
The \gls{LPM}, on the other hand, does not provide a reliable estimate.

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.75\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/figs/MC-runlength.tikz}
  %\input{figures/runLength.tikz}
  \caption[Estimated $\gamma$ versus measurement time.]{This Monte Carlo simulation shows that the $\Hinf{}$ norm~\legref{leg:runlength-true} is underestimated significantly for short experiments ($N<20\timeconst$) by $\expectedValue{\gammaAtGrid}$~\legref{leg:runlength-frf} and the \gls{LPM}~\legref{leg:runlength-LPM}.
  However, the proposed $\widehat{\infnorm{\Delta_{\LRM}}}$~\legref{leg:runlength-LRM} is already reliable from much shorter experiments ($N \geq 4 \timeconst$). A single observation for $N=97$~\legref{leg:runlength-special-case} is shown in \figref{fig:lrmhinf:exampleIntergrid}. The shaded areas show the $\pm \sigma$ intervals which are due to the noise.
  }
\label{fig:lrmhinf:MC-run-length}
\end{figure}
